Tables/Graphs for Article

### 2018-01-03 article/draft1.tex
combined univariate results tables

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ \hline
  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ \hline
  Number of characters in a question's text (untransformed) & 6.9472e-12 \\\hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ \hline
  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ \hline
  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ \hline
  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ \hline
  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ \hline
  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Day of the week the question was posted & 7.8677e-4 \\ \hline
  Device category & 0.00 \\ \hline
  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ \hline
  Whether or not the question's text is in all lower case & 1.5400e-7 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ \hline
  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\ \hline

\end{tabular}
\label{table:cresults}
\end{table}

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{3}{5cm}{Average number of characters in each questions tags}
  & Untransformed & 2.6115e-2 \\ 
  & Log & NA \\
  & Square root & 2.9999e-4 \\ \hline
  \multirow{3}{5cm}{Average frequency score of a question’s tags}
  & Untransformed & 1.2706e-08 \\
  & Log & NA \\
  & Square root & 1.4642e-11 \\ \hline
  \multirow{3}{5cm}{Number of characters in a question's text}
  & Untransformed & 6.9472e-12 \\
  & Log & 0.00 \\
  & Square root & 1.1102e-16 \\ \hline
  \multirow{3}{5cm}{Number of characters in the user-defined device title}
  & Untransformed & 6.5304e-3 \\
  & Log & NA \\
  & Square root & 2.2914e-4 \\ \hline
  \multirow{3}{5cm}{Ratio of the number of line breaks to the number of characters in a question's text} 
  & Untransformed & 1.3988e-7 \\
  & Log & NA \\
  & Square root & 1.1488e-11 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

Each training set contained 6208 questions, and each test set contained 1552 questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

>>>>

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | p{2.5cm} | p{2cm} |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & *Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
  & Untransformed & 2.611529e-02 \\ 
  & *Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
  & Untransformed & 6.947221e-12 \\
  & *Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
  & Untransformed & 6.530431e-03 \\
  & *Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & *Square root & 1.148792e-11 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{| p{7.5cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\label{table:univariate_results}
\end{table}

Each training set contained 6208 questions, and each test set contained 1552 questions. Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
